\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-08 paper/main.tex
microAUC

We evaluate all models on their recommended splitting scheme choice,
hyperparameters and fold among for cross-validation, measuring their
respective AUROC score. We eventually assess each model, by performing
a protein-wise cross-validation determining (macro) AUROC and
$MicroAUC_p$. For this we allow stratification for the training
process, but not for the validation and testing phase, as real world
scenarios are rather imbalanced. This however, only impacts the not
considered area under precision recall curve (AUPRC) and not the Macro
AUROC score, while also supporting the expressiveness of $MicroAUC_p$
with more data points.

@@

The results of this first analysis are summarized in the upper part of Figure \ref{tab:Results}.

>>>>

We evaluate all models on their recommended splitting scheme choice,
hyperparameters and folds in cross-validation, measuring their
respective AUROC. We further evaluate each model by performing a
protein-wise cross-validation determining (macro) AUROC and
$MicroAUC_p$. For this evaluation we allow stratification for the
training process but not for the validation and testing phase as
real world applications of these models would have to deal with
imbalanced data.

\todo[inline]{Merge the tables; add \name model to table to allow
  DIRECT comparison:}
The results of the analysis are summarized in the upper part of Figure
\ref{tab:Results}.

\todo[inline]{Discussion:}
The lack of stratification, only impacts the not
considered area under precision recall curve (AUPRC) and not the Macro
AUROC score, while also supporting the expressiveness of $MicroAUC_p$
with more data points.

@@
